\documentclass{article}
\usepackage{algpseudocode}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{color}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    filecolor=blue,      
    linkcolor=blue,
    urlcolor=blue,
}
\usepackage{parskip}
\title{Supervisory control assignment}
\author{Alberto Damo, Alessandro Pirolo, Pietro Zenezini}
\begin{document}
\pagenumbering{gobble}
\maketitle
\newpage
\pagenumbering{roman}
\tableofcontents
\newpage
\pagenumbering{arabic}
\section{Introduction}
The aim of the project is to model a plant
where a yellow and a blue rover move on a 3 $\times$ 5 grid.

$(1,1)$ represents the leftmost topmost tile, whereas $(5,3)$ the rightmost downmost one.

All of the movements are controllable, except for the ones
occurring on $(2,2)$.

Each rover has six units of energy in its battery and looses one of those
whenever it moves.

The grid has two charging stations at tiles $(1,1)$ and $(4,2)$
and rovers can charge their batteries whenever they reach those tiles.

The whole plant should respect these requirements:
\begin{enumerate}
    \item ``Both rovers never run our of battery on tiles that do not have a charging station"
    \item ``Both rovers must always alternate the use of the charging stations in $(1,1)$ and $(4,2)$ regardless of which is used first"
    \item ``Rovers don't collide with each other" (i.e., they are never simultaneously on a same tile)
\end{enumerate}

\section{Plant}
\subsection{Rovers}
Each rover is modelled by a finite-state automaton
where each state represents a tile of the grid.
The initial state represents the tile where the rover begins its path.
For the yellow rover initial state is $(1,1)$, whereas
for the blue one is $(4,2)$.
Every state is marked.

If the rover can reach a tile $(x', y')$ from a tile $(x, y)$
making a specific movement, then there is an edge labelled
with that movement from state $(x, y)$ to state $(x', y')$.

\paragraph{Example}
\textit{State encoding initial tile for the yellow rover}
\begin{verbatim}
location ONE_ONE: initial; marked;
    edge down_yellow goto ONE_TWO;
    edge right_yellow goto TWO_ONE;
    edge charge_yellow;
\end{verbatim}

\newpage

\subsection{Batteries}
Each battery is modelled by a finite-state automaton
where each state represents an energy level of the whole charge.
The initial state represents full charge and is the only marked one.

Every state has an edge to the one encoding the next minor energy level
for each of the rover's moves
and an edge to the initial state for the charge event.

\paragraph{Example}
\textit{State encoding full charge for the yellow rover}
\begin{verbatim}
location FULL: initial; marked;
    edge up_yellow goto FIVE;
    edge down_yellow goto FIVE;
    edge left_yellow goto FIVE;
    edge right_yellow goto FIVE;
    edge unc_up_yellow goto FIVE;
    edge unc_down_yellow goto FIVE;
    edge unc_left_yellow goto FIVE;
    edge unc_right_yellow goto FIVE;
    edge charge_yellow goto FULL;
\end{verbatim}

\section{Requirements}

\subsection{Requirement 1}
Since the only marked state for the battery automaton
is the one representing full charge,
any sequence of events which leads the system to a configuration
where a battery is not fully charged is not allowed.
So is the supervisor synthesis algorithm itself which enforces the
requirement by removing all the edges which may cause those executions.
In other words, there is no need to provide an explicit automaton for this requirement.

\subsection{Requirement 2}
Requirement is decomposed in two sub requirements, namely:
\begin{enumerate}
    \item ``Yellow rover must always alternate the use of the charging stations [...]''
    \item ``Blue rover must always alternate the use of the charging stations [...]''
\end{enumerate}
The automatons for the two requirements are isomorphic.

Each automaton has three sets of states:
\begin{enumerate}
    \item The one tracking the fact that rover has not charged its battery yet
    \item The one tracking the fact that rover has charged its battery in $(1,1)$
    \item The one tracking the fact that rover has charged its battery in $(4,2)$
\end{enumerate}

The first set is a copy of the rover automaton, but slightly modified.
As a matter of fact whenever a rover uses a charging station in $(x, y)$
the automaton enters the set of state which tracks that event.
In that set edges labelled with charging events are allowed only
for the tile where the unused charging station is.

\paragraph{Example}
\textit{Some snippets from the sub-requirement for the yellow rover}
\begin{verbatim}
location ONE_ONE: initial; marked;
    edge right_yellow goto TWO_ONE;
    edge down_yellow goto ONE_TWO;
    edge charge_yellow goto ONE_ONE__CHARGED_A;
\end{verbatim}
[...]
\begin{verbatim}
    location ONE_ONE__CHARGED_A: marked;
        edge right_yellow goto TWO_ONE;
        edge down_yellow goto ONE_TWO;
\end{verbatim}
[...]
\begin{verbatim}
location FOUR_TWO__CHARGED_A: marked;
    edge left_yellow goto THREE_TWO__CHARGED_A;
    edge right_yellow goto FIVE_TWO__CHARGED_A;
    edge up_yellow goto FOUR_ONE__CHARGED_A;
    edge down_yellow goto FOUR_THREE__CHARGED_A;
    edge charge_yellow goto FOUR_TWO__CHARGED_B;
\end{verbatim}
[...]

\textit{Note that the automaton is automatically generated by a JavaScript program}

\subsection{Requirement 3}
In order to respect this requirement, two conditions must always be verified in the system
\begin{enumerate}
    \item Rovers must not ``share" the same tile
    \item If a rover is on tile $(2,2)$, then the other one cannot be in an adjacent tile,
          since movements from $(2,2)$ are uncontrollable and so a collision with the adjacent rover may happen
\end{enumerate}
Each state of the automaton enforcing this requirment is of the form

$(x_{y}, y_{y}, x_{b}, y_{b})$, where:
\begin{itemize}
    \item $x_{y}$ and $y_{y}$ encode the yellow rover's coordinates
    \item $x_{b}$ and $y_{b}$ encode the blue rover's coordinates
\end{itemize}

\newpage

Each state is such that
\begin{enumerate}
    \item $x_{y} \neq x_{b} \land y_{y} \neq y_{b}$
    \item No edge which leads to ``dangerous'' configurations starts from it
\end{enumerate}

\textit{Note that the automaton is automatically generated by a JavaScript program,
    which basically checks all the possible coordinate configurations
    and discards all the edges leading to the ``wrong" ones according to the specified constraints.
}

\end{document}